---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pegap

<!-- badges: start -->
<!-- badges: end -->

`pegap` is an R package made to bridge the gaps in private equity portfolio analysis. It contains functions for calculating vintage year diversification, forecasting unfunded capital call liabilities, and visualising portfolios.

## Installation

``` r
# install.packages("pak")
pak::pak("ADC-405-S26/pegap")
```

## Functions

`pegap` has 3 main functions:

- `vintage_diversification_score()` — scores how concentrated a PE portfolio is across vintage years using HHI
- `unfunded_liability_schedule()` — forecasts future capital calls across a 5-year schedule with a preset drawdown curve
- `portfolio_plot()` — visualises portfolio progress by vintage year as a scatterplot

## Examples

```{r example, message = FALSE}
library(pegap)

vintage_diversification_score(
  fund_names = c("Fund A", "Fund B", "Fund C"),
  vintage_years = c(2019, 2020, 2019),
  committed_capital = c(10000, 15000, 8000)
)

unfunded_liability_schedule(code_script)

portfolio_plot(code_script)
```
