---
title: "Introduction to pegap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to pegap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

```{r setup}
library(pegap)
```


## Motivation

RStudio currently does not have extensive packages for PE Portfolio Analysis. This package aims to bridge a couple of those gaps.

## Dataset

`pegap` contains a pre-built simple dataset to practice with containing 5 fake funds' information.

```{r}
code_script
```
The dataset contains five variables:
- `fund` — name of the fund
- `vintage_year` — year the fund began investing
- `commitment` — total capital committed in USD ($)
- `called` — capital called to date in USD ($)
- `recallable` — recallable distributions in USD ($)

## Vintage Diversification Score

Quantifies the risk of weighting portfolios to heavily on one year using the Herfindahl-Hirschman Index (HHI). HHI is scaled from 0-1, multiplied by 100 to get a more intuitive score. The formula also accounts for the number of vintage years such that a portfolio with only 2 vintages would be able to reach a score of 100 (which it wouldn't do normally).

Usually, HHI is counter-intuitive, in that a low HHI is better. Using my scoring formula, the 
inverse is true: a score of 100 means perfect diversification across all years whereas lower scores represent intense concentrations in one or few years.

```{r}
vintage_diversification_score(
  fund_names = code_script$fund,
  vintage_years = code_script$vintage_year,
  committed_capital = code_script$commitment
)
```

**Note: when HHI>0.25, a warning message displays.**

## Unfunded Liability Schedule

Forecasts expected capital calls over a 5-year timeline using a realistic preset deployment curve (Year1-Slow, Year3-Peak) It calculates each fund's current unfunded liability (`commitment - called + recallable`) and distributes it across five years in a table. The table shows the total
current unfunded liability, and then shows the break down with appropriately labeled headers.

Unfunded liability schedules help inform both investors and fund managers when capital will be needed (in other words how much investors owe the fund manager in a given year). This structure allows investors to hold onto their own assets, only liquidating when necessary (thus allowing them to increase personal wealth with funds that would otherwise be sitting around doing nothing). This is important because PE funds typically make investments that require longer maturity timelines, meaning there is no reason to draw on the investors' capital until a significant transaction occurs.

The deployment curve is defined as: 

* Year 1: 5% 
* Year 2: 20%
* Year 3: 35% 
* Year 4: 25% 
* Year 5: 15%

```{r}
unfunded_liability_schedule(code_script)
```

## Portfolio Plot

Provides a visualisation of the portfolio as a scatterplot. Each point represents a fund, size shows total commitment and colour shows deployment progress. The x-axis shows vintage year, and the y-axis shows remaining unfunded commitment. It calls upon ggplot2's `theme_classic()`, and has automatic labels for the x-axis, y-axis, legend (size & colour).

The colour scale is pre-defined as: 

* High (75% or more called): Dark Green
* Middle (45%-70% called): Orange
* Low (Less than 45% called): Red

```{r}
portfolio_plot(code_script)
```


