---
title: "Introduction to pegap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to pegap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pegap)
```


##Motivation
RStudio currently does not have extensive packages for PE Portfolio Analysis. This package aims to bridge a couple of those gaps.

##Dataset
`pegap` contains a pre-built simple dataset to practice with containing 5 fake fund information.

```{r}
code_script
```
The dataset contains five variables:
- `fund` — name of the fund
- `vintage_year` — year the fund began investing
- `commitment` — total capital committed in USD ($)
- `called` — capital called to date in USD ($)
- `recallable` — recallable distributions in USD ($)

##Vintage Diversification Score
Quantifies the risk of weighting portfolios to heavily on one year using the Herfindahl-Hirschman Index (HHI). 
A score of 100 means perfect diversification across years.
```{r}
vintage_diversification_score(
  fund_names = code_script$fund,
  vintage_years = code_script$vintage_year,
  committed_capital = code_script$commitment
)
```

**Note: when HHI>0.25, a warning message displays.

##Unfunded Liability Schedule
Forecasts expected capital calls over a 5-year timeline using a realistic preset deployment curve (Year1-Slow, Year3-Peak)
It calculates each fund's current unfunded liability (`commitment - called + recallable`) and distributes it across five years

```{r}
unfunded_liability_schedule(code_script)
```

##Portfolio Plot
Provides a visualisation of the portfolio as a scatterplot. 
Each point represents a fund, size shows total commitment and colour shows deployment progress.
```{r}
portfolio_plot(code_script)
```
The x-axis shows vintage year, and the y-axis shows remaining unfunded commitment.


